BivData_Setup

### 2020-01-20 src/BivData_Setup.Rmd
work on draft for Bivdata analysis

@@

#test this part of the function
#I think most of these cell lines have been left out of the final DF
fullBivData <- fullBivData[!(fullBivData$fileName %in% MultiCells), ]
#save these number measures to report

@@

@@

fileName, Object_ID, box.number, centromere_ABS, centromere_PER
chromosome length, SC.pass, Foci.pass, hand.foci.count, 
F1, F2, F3, F4, F1_per, F2_per, F3_per, F4_per, IFD
mouse, strain, category, subsp,

@@

@@

@@

@@

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData.RData")
#save.image("data/BivData_4_PCA.RData")

>>>>

ToDo:

Add the new curated data.

@@

#test this part of the function
#I think most of these cell lines have been left out of the final DF
#fullBivData <- fullBivData[!(fullBivData$fileName %in% MultiCells), ]
#save these number measures to report

@@

- number of pass.SC w/out foci position data

- number of foci with 'faint' mentioned in the notes

@@

fileName, Object_ID, box.number, centromere_ABS, centromere_PER
chromosome length, SC.pass, Foci.pass, hand.foci.count, 
F1, F2, F3, F4, F1_per, F2_per, F3_per, F4_per, IFD

telomere_dist, cent_dist,

mouse, strain, category, subsp,

@@

```{r telo.cent_dist, echo=FALSE}

#code for cal1 the telomere distance
#space between last foci and telomere end

#telo_dist <- if(hand.foci = 1){
          #SC.Length - F1
#}
#elseif(hand_foci == 2){ #SC.length - F2}

#code for centromere
#space between first foci and centromere/centromere-end

#cent_end_dist
#cent_dist
```

@@

#make sure the this MELT_Curated_BivData.PER is made
#

@@

This is proof that the plot codes work, but move the figures in the analysis doc. remeber this is just data-setup.

think about weighing the density plots by the number of bivalents per category...

@@

# Save

@@

#save Rdata
save.image("~./MLH1repo/data/CleanBivData_1.20.20.RData")
#save.image("data/BivData_4_PCA.RData")
